This is the background

\section{Pulse Compression}
\label{pc}
The goal for radar signals is high sensitivity, which means a high signal-to-noise ratio (SNR), and high resolution. In order to get a high SNR,
the more energy can be put on target, the better the sensitivity. For a radar operating in transmitter saturation, that means the longer the
transmitted pulse is, the more energy is transmitted. 
Unfortunately, pulse length is inverse proportional to the resolution, so the longer the pulse, the larger the resolution volume will be.
Pulse compression is a way to decouple the relationship between SNR and resolution by controlling the duration and bandwidth separately.

The use of matched filter allows pulse compression since its output is the autocorrelation function of the transmit signal. This allows the design of
waveforms such that they are narrowly focused in a narrow main lobe, with low sidelobes to concentrate the signal energy in the main lobe (\cite{Richards:2005}).

\section{Linear Frequency Modulation}
\label{s_lfm}
In Pulse Compression, the frequency inside the pulse is modulated linearly (for Linear FM, or LFM) or non-linearly over a certain bandwidth. It is defined as:
\begin{equation}
\label{LFM}
x(t) = e^{j \pi \beta t^2 / \tau} = e^{j \theta (t)},\ \ 0 \leq t \leq \tau
\end{equation}

The spectrum of such a LFM waveform approaches the shape of a rectangle that is becomes better defined as the $\beta\tau$ ratio increases. The matched 
filter response of a rectangular waveform is a sinc function with Rayleigh resolution of approximately $1/\beta$ (\cite{Richards:2005}).


The result is an increase in the ambiguous range $r_a$.

The LFM effect is a consequence of a Ambiguity Function property, as follow:

If $u(t)$ has an added phase that changes quadratically, i.e. $u^{'}(t) = u(t) e^{j\pi kt^2}$, which is equivalent to a linear frequency modulation
because $\omega(t) = \frac{d}{dt}\phi(t)$, the resulting AF is $|\chi(\tau,f_d-k\tau)|$.


TODO: figures


The slow drop-off of peak in the AF makes LFM pulse compression very Doppler tolerant, which make it convenient for radar applications
that have to deal with high-velocity targets. Add to that the ease of implementation in analog hardware and we have a simple way to 
improve our radar's performance.

\section{Pulse Compression with binary codes}
One alternative to \ref{s_lfm} is the use of binary, or in our case, quadrature codes. With it, a subsection of each pulse is
shifted in phase by $e^{jk \pi}$, where $k=(0, \frac{1}{2}, 1, \frac{3}{2})$. The performance of each code is measured by calculating
the Integrated Sidelobe Level (ISL), which is defined as (\cite{Keeler:1999}):

\begin{equation}
\label{ISL}
ISL = 10 \log \left(\frac{\sum\limits_{j} |m_k|^2}{\sum\limits_{k} |s_j|^2}\right)
\end{equation}

where $s_j$ is the power of the $j^{th}$ sidelobe, and $m_k$ the power of the $k^{th}$ mainlobe.

The higher the ISL, the better the performance of the code.

\section{Binary Phase Codes compared to Frequency Modulation}

\section{Bandwidth for Binary Phase Codes}
Use less bw?

\section{Use of Phase Codes in Profilers}
why are they using it?

\section{Military Radars' use of Frequency Modulation} 
Since LFM is simply taking advantage of a property of the AF, it was the earliest way of getting increased sensitivity. It's fairly
simple to implement in analog hardware and very Doppler tolerant due to the slow decrease in slope.

\section{Amplitude Tapering compared to Non-linear Frequency Modulation}

\section{Doppler Effect for Atmospheric Radar}
One question for pulse compression performance is the effect of a Doppler shift on matched filter in the receiver. Any received signal that
has been affected by a Doppler shift will cause a mismatch in the matched filter of the receiver. This is especially pronounced the higher the
target velocity is. For atmospheric weather radars, we observe targets that usually move 25 m/s at maximum, causing a Doppler shift of
$f_d = \frac{2v}{\lambda} = \frac{50}{0.1} = 500\ Hz$ for S-band.

This mismatch effect on the matched filter has been quantified by Kelly and Wishner as follows (\cite{Kelly:1965}):

For a signal of length T, a target of velocity v, and signal bandwidth B, the return Doppler-shifted signal can be written as $T(1-\frac{2v}{c})=T-\Delta T$. If 
$\Delta T$ is much smaller than $T$, i.e.  $\Delta T << \frac{1}{B}$, the mismatch due to the Doppler effect can be neglected. In other words, 
$\frac{2v}{c}BT << 1$. For a $1\mu s$ pulse at 5 MHz bandwidth moving at 30 m/s, $0.001 << 1$ is true, so the Doppler effect can be ignored.

The pulse compression ratio, $BT$, is not equal to unity, so the mismatch in the filter is compounded for highly compressed pulses, which also makes sense
intuitively.
