\documentclass[letter,12pt,dissertation]{OUdissertation5} %for Ph.D. disseration style
%\documentclass[letter,12pt,thesis]{OUdissertation5} %for M.S. thesis style
\usepackage{graphicx} %allows .eps and .epsi graphics to be inserted
\usepackage{epic} %allows use of latex graphics
\usepackage{eepic} %allows use of latex graphics
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{psfrag}
\usepackage{float}
\usepackage{bar}
% Brian added this on July 15 2006 from suggestion of Di Jin:
\usepackage[centerfoot]{pageno}

%\usepackage{harvard} %use with agsm.bst, see near end
%\newcommand{\citet}[1]{\citeasnoun{#1}} %use this with harvard 
%\newcommand{\citep}[1]{\cite{#1}} %use this with harvard 

\usepackage{natbib} %with amermeteorsoc.bst
%% For AMS,citations should be of the form ``author year''  not ``author, year'':
\bibpunct{(}{)}{;}{a}{}{,}

\newcommand{\be}{\begin{equation}} %these definitions save typing
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[3]{\frac{\partial^{2}#1}{\partial#2 \partial#3}}


\begin{document}
\title{ USING \LaTeX\  TO WRITE \\ A DISSERTATION AT O.U.}
\author{BRIAN FIEDLER}
\depositdate{1998}
\majorfield{SCHOOL OF METEOROLOGY}
\memberone{Prof. Albert Einstein}
\membertwo{Prof. Enrico Fermi}
\memberthree{Prof. Alfred E. Newman}
%next two members are used in dissertation
\memberfour{Dr. Homer Simpson}
\memberfive{Dr. Strangelove}
%another member is possible, but you must hack OUdissertation.cls
\membersix{Dr. Spock}
%%%%
\begin{preface}
%\prefacesection{Dedication} %Dedication must be without a pagenumber, see end of this file.
%This dissertation is dedicated to Donald Knuth and Linus Torvalds.
\prefacesectionX{Dedication}
This dissertation is dedicated to Donald Knuth and Linus Torvalds.

A dedication page is optional in the OU dissertation.  
This section is not allowed to have a printed pagenumber, nor is it allowed to
increment the page number counter. This is why we use the hacked \verb+\prefacesectionX+ for
the Dedication, rather \verb+\prefacesection+.
\prefacesection{Acknowledgements}
I would like to thank Prof. Einstein and Prof. Fermi
for their expert advice  and  patience.  Their sacrifice
was enormous, considering the fact that I got a D in
freshman physics --- and I never really got much better after that.
%must leave a blank line next to avoid bug:

\tableofcontents
\listoftables
\listoffigures
\prefacesection{Abstract}
 In 1998, I hacked the \texttt{OUdisseration.cls} file from the 
{\tt USCthesis.cls} file that I grabbed from the web.
As of April 21, 2009, this ``dissertation'' uses the \texttt{OUdisseration5.cls} to define the
document class.
The comments inside \texttt{OUdissertation5.cls} describe the changes.
(You may see a bug here with the text extending past the margin.)
 
I put this example ``dissertation'' together for the benefit of
the students at the University of Oklahoma, who can use it as a 
template for their own work.   Depending on the demand of the users,
maybe someday I will clean this up.  {\it Caveat user}.
\end{preface}
\chapter{Introduction}
\label{intro}
\input{intro}
\chapter{Mostly {\tt .eps and .pdf} examples}
\label{eps_pdf_examp}
\input{eps_pdf_examp}
\chapter{Other examples}
\label{other}
\input{other}
%
%\references{agsm}{myreferences}
\references{amermeteorsoc}{myreferences}
%comment out the next four lines if you don't have an appendix
\appendix
\chapter{A Long Proof}
\OUdoublespace
\input{appex}
\end{document}
