%\documentclass[letter,12pt,dissertation]{OUdissertation5} %for Ph.D. disseration style
\documentclass[letter,12pt,thesis]{OUdissertation} %for M.S. thesis style
\usepackage{graphicx} %allows .eps and .epsi graphics to be inserted
\usepackage{epic} %allows use of latex graphics
\usepackage{eepic} %allows use of latex graphics
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{psfrag}
\usepackage{float}
\usepackage{listings}
\usepackage{siunitx}


% for hyperlinks
%\usepackage{hyperref}

%\floatstyle{boxed} 
%\restylefloat{figure}

%\usepackage{bar}
% Brian added this on July 15 2006 from suggestion of Di Jin:
\usepackage[centerfoot]{pageno}

%\usepackage{harvard} %use with agsm.bst, see near end
%\newcommand{\citet}[1]{\citeasnoun{#1}} %use this with harvard 
%\newcommand{\citep}[1]{\cite{#1}} %use this with harvard 

\usepackage{natbib} %with amermeteorsoc.bst
\usepackage{amsmath}
%% For AMS,citations should be of the form ``author year''  not ``author, year'':
\bibpunct{(}{)}{;}{a}{}{,}

\newcommand{\be}{\begin{equation}} %these definitions save typing
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\pd}[2]{\frac{\partial#1}{\partial#2}}
\newcommand{\pdd}[3]{\frac{\partial^{2}#1}{\partial#2 \partial#3}}
\newcommand{\imgsize}{440 pt}
\newcommand{\imgsizes}{340 pt}


\begin{document}
\title{OPTIMAL WAVEFORM DESIGN FOR WEATHER RADARS}
\author{CHRISTOPH KOEHLER}
\depositdate{2011}
\majorfield{SCHOOL OF ELECTRICAL AND COMPUTER ENGINEERING}
\memberone{Dr. Robert D. Palmer, Chair}
\membertwo{Dr. Boonleng Cheong}
\memberthree{Dr. Mark Yeary}
%next two members are used in dissertation
\memberfour{Dr. Guifu Zhang}
%\memberfive{Dr. Strangelove}
%another member is possible, but you must hack OUdissertation.cls
%\membersix{Dr. Spock}
%%%%
\begin{preface}
%\prefacesection{Dedication} %Dedication must be without a pagenumber, see end of this file.
%must leave a blank line next to avoid bug:

\tableofcontents
%\listoftables
\listoffigures
\prefacesection{Abstract}
Most of the literature about radar waveforms has been done in the context of application other than weather.  This
thesis will focus the discussion on pulse compression for weather radar applications. First, a general overview of using
radar for weather applications is given, followed by a brief discussion of general waveform design, in particular the
different components of a waveform that can be manipulated for its design. Next, the concepts of pulse compression will
be presented and the need for pulse compression explained.  Then, various different waveforms, like rectangular pulses,
phase coded, linear frequency modulated, and non-linear frequency modulated signals will be examined in regards to their
ambiguity function, which serves as the basis for performance metrics.  Each will be quantified in respect to integrated
sidelobe level, peak sidelobe level, and range resolution. Further, amplitude tapering will be applied to determine its
performance benefits.  For the non-linear frequency modulated waveforms, the frequency sweep function is parameterized
and optimal values for weather applications are presented. Lastly, the effects of a system impulse response on the
signal will be discussed and their performance analyzed.
\end{preface}
\chapter{Introduction}
\label{intro}
\input{1introduction}
\chapter{General Waveform Design}
\label{genwaveform}
\input{2genwaveform}
\chapter{Pulse Compression}
\label{chap:pulsecompression}
\input{3pulsecompression}
\chapter{Performance of Pulse Compression}
\label{performance}
\input{4performance}
\chapter{Waveform Optimization}
\label{chap:optimization}
\input{5optimization}
\chapter{Conclusion and Future Work}
\label{conclusionfuture}
\input{6conclusionfuture}
%
%\references{agsm}{myreferences}
\references{amermeteorsoc}{references}
%comment out the next four lines if you don't have an appendix
\appendix
\chapter{Code Listing}
\label{app:code}
\OUdoublespace
\input{app1code}
\end{document}
